\chapter{Conclusion}
The designed Smart helmet ensures the safety of the rider
by making it necessary to wear helmet, and also ensures
that the rider hasn’t consumed alcohol more than the
permissible limit. If any of these prime safety rules are
violated, the proposed system will prevent the biker from
starting the bike. The system also helps in efficient
handling of the aftermath of accidents by sending a SMS
. This
ensures that the victims get proper and prompt medical
attention, if he/she met with an accident.

\vspace{.9cm}
It is very useful as it has following benefits: \vspace{.3cm}

\section{Driver Safety}

Smart helmets have upgraded hardware. They mostly use EPS padding in the inner lining that is more shock-proof. 

Smart software allows for SOS buttons, tracking riders, and sending automatic alerts to emergency contact during an accident.
\vspace{.9cm}

\section{Enhanced Driving Experience }

- Enjoy the benefits of voice assistants while driving.

- See the rearview video in the HUD display. Listen to audio alerts for turn-by-turn navigation.

- Stay connected with multiple riders with smart helmets.

- Experience a great music system in the helmets. 
\vspace{.9cm}

\section{Protection Against Head Injuries}

Hard hats type safety helmets are designed specifically to provide protection to the workers from injury penetration, electric injuries and strong head impacts, which can be caused because of flying or falling objects. These safety helmets also provide protection against fixed objects and electrical conductors that may lead to injury. You can easily buy such kind of safety helmets online at very affordable price.
\vspace{.9cm}

\section{Protection Against Slips And Fall}

Wearing safety helmets while working in a liquid based FMCG or a chemical unit ensures that even if the work slips or falls accidentally the chances of causing a head injury will be minimal.
\vspace{.9cm}

\section{Increases Chances of Survival In Accidents}

If a work unit faces accidental situations like rolling over of a truck or mishandling of any industrial equipment, in such scenario if workers is wearing safety helmet his chances of getting hurt will remain minimal.
\vspace{.9cm}
\section{Flying Objects}

A motorcycle helmet shields the eyes and face from flying objects like rocks, gravel and twigs. It also protects the rider from insects.
\vspace{.9cm}

\section{Weather}

A motorcycle helmet offers protection from the weather. For instance, it has a visor that cuts down the glare from the sun. It also keeps the face warm in frigid weather and keeps water out when it rains.