\chapter{Suggestions}
Smart helmets have added features that can help riders drive safer, more efficiently and enhance their driving experience.\vspace{.3cm} 

Smart helmets can include some or all of these features:
\section{Bluetooth connectivity}
\begin{itemize}
	\item \textbf{Hands-free communication. }When you're riding a motorcycle, it's vital to keep your eyes on the road and your hands on the bars. The best motorcycle helmets with Bluetooth let you interact with electronic devices while staying focused on the riding experience.
	\item \textbf{Reduced distraction. }A Bluetooth-integrated motorcycle helmet makes using a smartphone, GPS navigation system, or other electronic devices safer than trying to manipulate these devices while you’re in traffic.
	\item \textbf{Convenience.} Bluetooth technology is easy to use, and it doesn't consume a lot of power. You can listen to your favorite songs, answer phone calls, or converse with riding companions by simply hitting a switch.
\end{itemize}
\section{WiFi Connectivity}
\begin{itemize}
	\item \textbf{Social connections:} Like the phone and other cutting-edge communication channels at the time, the Internet is invaluable for keeping the world connected. To be fair, you probably won’t miss a whole lot without the Internet in your car, but having a consistent connection still pays off.
	
	\item \textbf{Remote work:} Without a doubt, the bulk of demand for WiFi on the road comes from people who work remotely.
	
	
\end{itemize} 
\section{Voice assistance }
\begin{itemize}
	\item Make a phone call
	\item Ask for direction
	\item Send a text
	\item Start playing music
	\item Ask about restaurants
	\item Start playing radio stations
	\item Control smart home devices
\end{itemize}
\section{Make, Accept and Reject Calls }
\begin{itemize}
	\item If your phone has Bluetooth enabled on it, it will easily connect to any hands-free device. This means that you have the ability, at the very least, to talk on your mobile phone while driving. If your device has voice activation capabilities, modern day wonders make it possible for you to give commands to your phone via your Bluetooth hands-free device which allows for you to make, accept and reject calls
\end{itemize}
\section{Connect with smart devices }
\begin{itemize}
	\item \textbf{Security:} Connected vehicles come equipped with several critical security features such as real-time location sharing/tracking, emergency SOS calls in case of an accident, roadside assistance in case of vehicle breakdown and much more. Apart from the onboard safety equipment, these smart safety features come in handy during tricky situations.
	\item \textbf{Vehicle to Vehicle Communication:}
	Vehicle-to-vehicle connectivity technology allows connected vehicles to communicate with each other. The V-2-V enables the sharing of vital information such as traffic movement, road conditions, speed limits and much more. V-2-V technology will be a critical part of autonomous vehicles, which are deemed as the future of mobility.
	\item \textbf{Hands-free communication. }When you're riding a motorcycle, it's vital to keep your eyes on the road and your hands on the bars. The best motorcycle helmets with Bluetooth let you interact with electronic devices while staying focused on the riding experience.
	\item \textbf{Social connections:} Like the phone and other cutting-edge communication channels at the time, the Internet is invaluable for keeping the world connected. To be fair, you probably won’t miss a whole lot without the Internet in your car, but having a consistent connection still pays off.
\end{itemize}
\section{Connect with other smart helmets and riders }
\begin{itemize}
	\item \textbf{Vehicle to Vehicle Communication:}
	Vehicle-to-vehicle connectivity technology allows connected vehicles to communicate with each other. The V-2-V enables the sharing of vital information such as traffic movement, road conditions, speed limits and much more. V-2-V technology will be a critical part of autonomous vehicles, which are deemed as the future of mobility.
\end{itemize}
\section{FM radio }
\begin{itemize}
	\item A FM Radio system allows you to listen to your favorite music whilst you are driving.
\end{itemize}
\section{Intercom }
\begin{itemize}
	\item Improved Communication
	\item Versatility
\end{itemize}
\section{Heads-up Display }
\begin{itemize}
	\item  Significant increase in the time the driver spends "eyes out"
	\item Simplifies the combined tasks of driving safely, monitoring the vehicle speed and performance and navigating to the destination
	\item Reduced driver fatigue in managing vehicle information while paying attention to the outside world
	\item Unique HUD capabilities enable the display of information coherent (conformal) with the outside world
	\item A HUD close to the driver's line of sight enables the intuitive display of enhanced features and dynamic real-time data
\end{itemize}
\section{Emergency Buttons }
\begin{itemize}
	\item Emergency Buttons can alert appropriate authorities in the event of a suspected wrongful behavior on the part of the driver, or an accident causing fatalities. So passengers can rest assured for a safe and secure commute
\end{itemize}
\section{Tracking systems}
\begin{itemize}
	\item \textbf{Improve Safety:}
	Not only will drivers be more responsible because they are aware of the monitoring, but fleet managers will know exactly where a vehicle is if it requires any assistance. Whether it’s a broken down engine or any emergency situation, fleet managers can send roadside assistance to help their driver.
	
	
	\item \textbf{Minimize Fuel Costs:}
	No one can control the price of gas, but one of the best benefits of tracking systems is the ability to observe a vehicle’s fuel consumption. The monitoring software will cut down on the amount of money spent on fuel by eliminating vehicle idling, driver speeding, any unauthorized usage, and gives fleet managers the ability to optimize driving routes.
	
	
	\item \textbf{Theft Recovery:}
	In the case of a vehicle theft, a tracking system is the best tool for any fleet company. Be notified with alerts and mapping data to help you identify whether the vehicle has been stolen and inform the authorities of its location to enable a quick recovery.
	
	
	\item \textbf{Lower Operational Costs:}
	Using tracking software allows fleet managers to see who is taking inefficient routes or using a vehicle for unauthorized purposes. Not only will it solve on the road issues, but it provides an accurate readout of the hours that drivers claim to have worked.
	
	
	\item \textbf{Increase Productivity:}
	Because of the ability to track drivers’ hours worked, this also allows fleet managers to make better use of an employee’s time. The tracking software shows exactly where your drivers are at all times and keeps record of what work they are doing at that time.
\end{itemize}
\section{Cameras }
\begin{itemize}
	\item \textbf{Record Your Favourite Rides}
	
	Wearing a helmet camera is a great way to record your favourite motorbike rides. Upload the video to your computer or media player or create a youtube motorcycle channel even and you will be able to enjoy and share all of the excitement all over again. Watching the rides back from the comfort of your armchair will also allow you to appreciate some of the things that you might not have had chance to dwell on during the continued journey.
	
	\item \textbf{Improve your skills}
	
	Having the ability to review your riding when you are off of the bike can give you the opportunity to improve your skills. Re-watching your rides will allow you to see what you have done well and what you may be able to improve on. Picking up on problems when you are sat in the house will allow you to make a conscious effort to correct those problems once you are back in the saddle. It is also possible to show your videos to an instructor so that they can comment on anything else that you might have missed when re-watching.
	
	\item \textbf{Share Your Rides}
	
	Recording videos of your rides will also give you the opportunity to share your rides with other. Motorbike riding can be a solitary experience, because no other rider will have exactly the same experience as you, even if you are riding along the same stretch of road at the same time. Being able to share your rides with others can also help you to develop your role in the motorcycle riding community.
	
	\item \textbf{Lower Insurance Costs}
	
	Some insurance providers are prepared to offer motorcycle riders lower insurance premiums if they are prepared to record all of their rides with a helmet camera. A helmet camera should be able to provide evidence if the rider is involved in any incidents whilst they are out on the road. The evidence which is recorded by these cameras can be used to help to find out who was at fault for a crash or accident. The insurance provider can also provide your footage to the defendant’s insurance provider if there are any disputes over who is responsible. In general, insurance providers also believe that people ride more safely when they are wearing helmet cameras for insurance purposes.
	
	\item \textbf{Protect Yourself}
	
	Wearing a helmet camera can help you to protect yourself from other drivers. Many car drivers do not give motorcycle riders enough space when they are on the roads and inattentive drivers can fail to spot bikers in their wing mirrors. However, bikers often get the blame for these incidents. Footage from a helmet camera can be used to protect you from these types of allegations and help to prove or disprove who was at fault in a personal injury claim.
	
	You can also submit your footage to the police if you are involved in any incident where another road user commits an offence and does not stop. Taking these users off of the road, even for a short amount of time can help to protect other motorcycle riders. Most helmet cameras also come with audio recording technology, so that you can get a record of any verbal altercations that occur whilst you are riding.
	
	\item \textbf{Deter Bad Behaviour}
	
	The simple presence of a visible helmet camera can help to deter some bad behaviour from other road users. When people see your camera they will realise that there is the possibility that their behaviour may be captured on camera. They will then modify their normal behaviour so that the footage will not end up showing them in a bad light. Riders with helmet cameras often find that other road users become less aggressive towards them.
\end{itemize}
\section{Audio Alerts }
\begin{itemize}
	\item Improved focus (due to localization of sound)
	\item Ability to multitask (due to separation of sound)
	\item Better situational awareness
	\item Faster response and reaction times
	\item Less need to take eyes off road to view display prompts
	\item More intuitive reactions requiring less concentration
	\item Greater passenger awareness
	\item Enhanced input when visibility is limited
	\item Optimized sound placement for hearing impaired
	\item Enhanced audio experience and “cool-factor”
\end{itemize}
\section{GPS Connectivity }
\begin{itemize}
	\item \textbf{Improved productivity and fewer calls to drivers}\\
	Whilst it’s important to be able to contact drivers about changes in pickups, deliveries and service calls, the frequent calls asking “Where are you now?” is highly distracting to the driver and is also a very inefficient use of the driver’s time and the time of your head office staff. Imagine the time wasted with a fleet of business vehicles.
	
	This greatly improves productivity, improves your profitability and reduces unnecessary phone calls to drivers.
	
	
	\item \textbf{Improved customer service with GPS vehicle tracking devices}\\
	Rather than giving customers approximate times, the main office can easily see exactly where the driver is now, and how far away from the customer they are.  This makes it very easy for the business to inform customers about pickup, delivery or service arrival times down to 5 minutes accuracy, if required.
	
	
	\item \textbf{OH\&S: health and safety of field staff and drivers}\\
	The whereabouts of your field staff especially during bad weather can be a real concern.
	
	Also too is not being able to reach a particular driver after a long period of time.  By seeing their location on a map from the data from the GPS vehicle tracking device and how long their vehicle has been stationery can at least make it easier and more timely to respond to any potential safety issue for the driver.
	
	
	\item \textbf{Fast vehicle recovery}\\
	If the unfortunate happens and one of your fleet vehicles is stolen, knowing it’s exact location using the GPS vehicle tracking device allows you (or the police) to recover your vehicle quickly thereby reducing vandalism and damage.  Also, quick response to theft greatly increases the likelihood of the vehicle’s recovery before it’s stripped down.
	
	\item \textbf{Reduce insurance costs}\\
	Insurance companies know the benefits listed above in regards to fast vehicle recovery so most of them will give you a insurance premium discount.  These savings can be significant.
	
	\item \textbf{Automatic theft / unauthorised use notification}\\
	If your vehicles are left at your work premises, yard, depot or some other frequent parking spot, you can receive instant, automatic notification by SMS text or email if your vehicle leaves that area.  That way you quickly know if one of your staff have moved the vehicle without your permission or if it is being stolen.
	
	\item \textbf{Reduced administration paperwork and other productivity benefits}\\
	As GPS vehicle tracking devices send frequent 3-4 minute location logs, key on and key off information is very simple with the report function to know the kilometres travelled each day – effectively replacing paper-based log books
	
	\item \textbf{Maximise your business vehicle assets}\\
	Using such reporting functionality you can see if any vehicles are being over or under utilised and make better business decisions of the use of these assets.  This is another efficiency boost for your business.
\end{itemize}

\section{Better Hardware }
\begin{itemize}
	\item \textbf{Protection Against Head Injuries}
	
	Hard hats type safety helmets are designed specifically to provide protection to the workers from injury penetration, electric injuries and strong head impacts, which can be caused because of flying or falling objects. These safety helmets also provide protection against fixed objects and electrical conductors that may lead to injury. You can easily buy such kind of safety helmets online at very affordable price.
	
	\item  \textbf{Protection Against Slips And Fall}
	
	Wearing safety helmets while working in a liquid based FMCG or a chemical unit ensures that even if the work slips or falls accidentally the chances of causing a head injury will be minimal.
	
	\item \textbf{Increases Chances of Survival In Accidents}
	
	If a work unit faces accidental situations like rolling over of a truck or mishandling of any industrial equipment, in such scenario if workers is wearing safety helmet his chances of getting hurt will remain minimal.
\end{itemize}